---
title: "Reproducible Research Peer assesment 1"
author: "A Lagarde"
date: "Saturday, January 17, 2015"
output: html_document
---

Loading and preprocessing the data
----------------------------------

```{r}
library(lattice)
data<-read.csv("activity.csv")
data$date<-as.Date(data$date)
dataNoNa<-na.omit(data)
```

What is mean total number of steps taken per day?
-------------------------------------------------

```{r}
dataDay<-aggregate(steps~date,data=dataNoNa,sum)
barplot(dataDay$steps,names.arg=dataDay$date,xlab="Date",ylab="Steps")
```

We calculate the median steps per day

```{r}
median(dataDay$steps)
```

and the mean per day

```{r}
mean(dataDay$steps)
```

What is the average daily activity pattern?
-------------------------------------------

```{r}
dataInt<-aggregate(steps~interval,data=dataNoNa,mean)
plot(dataInt,type="l")
dataInt$interval[which(dataInt$steps==max(dataInt$steps))]
```

The 5-minute interval, which on average across all the days in the dataset, contains the maximum number of steps is 835.

Inputing missing values
-----------------------

```{r}
naRow<-which(is.na(data$steps))
length(naRow)
```

2304 values are missing
We will fill those missing values with the mean of the 5mn intervals, and create a new dataset called dataFill

```{r}
dataFill<-data
dataFill$steps[naRow]<-dataInt$steps[match(dataFill$interval[naRow],dataInt$interval)]
```

We used these dataset to do the same histogram and calculations (median and mean) as in the first question

```{r}
dataDay2<-aggregate(steps~date,data=dataFill,sum)
barplot(dataDay2$steps,names.arg=dataDay2$date,xlab="Date",ylab="Steps")
median(dataDay2$steps)
mean(dataDay2$steps)
```

There is little impact on the calcul of the median and none on the mean

Are there differences in activity patterns between weekdays and weekends?
-------------------------------------------------------------------------

```{r}
dataFill$day<-as.numeric(format(dataFill$date,"%u"))
dataFill$we<-NA
dataFill$we[which(dataFill$day>5)]<-"weekend"
dataFill$we[which(dataFill$day<6)]<-"weekday"
dataFillInt<-aggregate(steps~interval+we,data=dataFill,mean)
xyplot(steps~interval|we,data=dataFillInt,type="l",scales=list(y=list(relation="free")),layout=c(1,2))
```
